Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 code.tex
code touch up

   //perform first tensor multiplication
   vect = permute(all_vect, _MM_PERM_AAAA);
   mat = _mm512_swizzle_ps(mat_ent, _MM_SWIZ_REG_AAAA);
   accu = _mm512_fmadd_ps(vect, mat, accu);

   //three more times with BBBB, CCCC, and DDDD
 }
 _mm512_storenrngo_ps(dom.result_vt+nb_mat*nb_vec*r, accu);  
\end{verbatim}
\end{center}
\end{figure}

>>>>

   //perform first tensor multiplication with AAAA pattern
   vect = permute(all_vect, _MM_PERM_AAAA);
   mat = _mm512_swizzle_ps(mat_ent, _MM_SWIZ_REG_AAAA);
   accu = _mm512_fmadd_ps(vect, mat, accu);

   //three more times with BBBB, CCCC, and DDDD patterns
 }
 _mm512_storenrngo_ps(dom.result_vt+nb_mat*nb_vec*r, accu);  
\end{verbatim}
\end{center}
\end{figure}
